A Large-Scale Study of the Use of Eval in R

### 2020-08-28 inst/paper/main.tex
Comment irrelevant stuff

\subsection{Consistency}

Here we talk about whether the same call site sees the same pattern

{\bf Polymorphic may not be the right word.}

We look at how \emph{polymorphic} the \c{expr} argument of \eval can be, \ie
how many different types of the resolved \c{expr} there are per call sites,
in Figure~\ref{fig:polymorphism}. \PercentMonomorphic of the call sites are
\emph{monomorphic}.

\begin{figure}[!h]
	\centering
    \includegraphics[width=\columnwidth]{polymorphism}
    \caption{Degree of polymorphism of \c{expr} per call sites.} \label{fig:polymorphism}
\end{figure}

\subsection{base}

There are 30 functions in \emph{base} that use \eval. Only five of them use \c{parse}, for legitimate reasons, such \c{source} and \c{sys.source} which load a file and then evaluate it, or \c{invokeRestartInteractively} which prompts the user for arguments to restart execution after an error.

We endeavored  to write these functions without \eval. \c{match.arg} appears in \MatchArgPercent of the \eval calls. It is used to get the arguments, possibly abbreviated, of a function. With one argument, as \c{match.arg(arg)}, it uses \c{eval} to infer them from a parent function's formal arguments. We can rewrite it using its version with two arguments, \c{match.arg(arg, choices)} where \c{choices} are the possible formal arguments of the function, as shown in Listing~\ref{code:matcharg}.

\begin{lstlisting}[caption={Rewriting \c{match.arg} without \eval}, label=code:matcharg]
f <- function(type=c("examples", "tests", "vignettes")) {
actual_type = match.arg(type)
...
}

f <- function(type=c("examples", "tests", "vignettes")) {
actual_type = match.arg(type, choices=c("examples", "tests", "vignettes"))
...
}
\end{lstlisting}

>>>>

%%\subsection{Consistency}
%%Here we talk about whether the same call site sees the same pattern
%%
%%{\bf Polymorphic may not be the right word.}
%%
%%We look at how \emph{polymorphic} the \c{expr} argument of \eval can be, \ie
%%how many different types of the resolved \c{expr} there are per call sites,
%%in Figure~\ref{fig:polymorphism}. \PercentMonomorphic of the call sites are
%%\emph{monomorphic}.
%%
%%\begin{figure}[!h]
%%	\centering
%%    \includegraphics[width=\columnwidth]{polymorphism}
%%    \caption{Degree of polymorphism of \c{expr} per call sites.} \label{fig:polymorphism}
%%\end{figure}
%%
%%\subsection{base}
%%
%%There are 30 functions in \emph{base} that use \eval. Only five of them use \c{parse}, for legitimate reasons, such \c{source} and \c{sys.source} which load a file and then evaluate it, or \c{invokeRestartInteractively} which prompts the user for arguments to restart execution after an error.
%%
%%We endeavored  to write these functions without \eval. \c{match.arg} appears in \MatchArgPercent of the \eval calls. It is used to get the arguments, possibly abbreviated, of a function. With one argument, as \c{match.arg(arg)}, it uses \c{eval} to infer them from a parent function's formal arguments. We can rewrite it using its version with two arguments, \c{match.arg(arg, choices)} where \c{choices} are the possible formal arguments of the function, as shown in Listing~\ref{code:matcharg}.
%%
%%\begin{lstlisting}[caption={Rewriting \c{match.arg} without \eval}, label=code:matcharg]
%%f <- function(type=c("examples", "tests", "vignettes")) {
%%actual_type = match.arg(type)
%%...
%%}
%%
%%f <- function(type=c("examples", "tests", "vignettes")) {
%%actual_type = match.arg(type, choices=c("examples", "tests", "vignettes"))
%%...
%%}
%%\end{lstlisting}
